\begin{rubric}{\textsc{Education}}

\entry*[$2021 - \hspace{0.125cm} \cdots$]%
	\textbf{\hl{Doctor of Philosophy (Ph.D.) --- Computer Science and Engineering.}}
    %
    \begin{enumerate}
        \item[\circled{1}] \textbf{Indian Institute of Technology Guwahati, Assam, India,} ~~\textit{jointly with}
        % \item[] \textit{jointly with}
        \item[\circled{2}] \textbf{Indian Institute of Technology (BHU) Varanasi, Uttar Pradesh, India.}
    \end{enumerate}
    Coursework grade: $8.75 / 10.00$
	\par Research area: \emph{Designing Machine Learning-based Security Scheme for Inside and Outside Mimicry Attack Detection in Industrial Internet of Things (IIoT) Networks.}
%
\entry*[$2019 - 2021$]%
	\textbf{\hl{Master of Technology (M.Tech.) --- Computer Science and Engineering.}\newline National Institute of Technology Durgapur (NIT Durgapur), West Bengal, India.}\newline Final grade: $9.28 / 10.00$
	\par Thesis title: \emph{A Game Theoretic Framework for Surplus Food Distribution in Smart Cities and Beyond.}
%
\entry*[$2006 - 2010$]%
	\textbf{\hl{Bachelor of Engineering (B.E.) --- Computer Science and Engineering.}\newline University Institute of Technology (UIT),\newline The University of Burdwan (BU), West Bengal, India.}\newline Final grade: $79.9\%$
%
\entry*[$2004 - 2006$]%
	\textbf{\hl{CBSE AISSCE (Class XII) --- Physics, Chemistry, Mathematics, Biology, English.}\newline Kendriya Vidyalaya Number $\mathbf{1}$, Saltlake, Kolkata, West Bengal, India.}\newline Final grade: $79.6\%$
%
\entry*[$\hspace{0.125cm} \cdots \hspace{0.125cm} - 2004$]%
	\textbf{\hl{CBSE AISSE (Class X).}\newline Kendriya Vidyalaya Number $\mathbf{1}$, Saltlake, Kolkata, West Bengal, India.}\newline Final grade: $82.8\%$
\end{rubric}