\begin{rubric}{\textsc{Miscellaneous Experience}}


\subrubric{\textsc{\underline{Certifications and Training}}}

\entry*[$2025$] \hl{\textbf{Active Participation in interactive training session (March 17):}} On \textit{Intellectual Property Rights (IPR) Awareness} organized by the \textit{Government of India}, and the \textit{Intellectual Property Rights (IPR) Cell, Indian Institute of Technology (BHU) Varanasi, India}, at the \textit{Indian Institute of Technology (BHU) Varanasi, India.}

\entry*[$2024$] \hl{\textbf{Active Participation in three-day International Workshop (July 01 to July 03):}} On \textit{Design Automation for Quantum Computing} organized by \textit{IEEE ComSoc Chapter, Guwahati (Kolkata Section)}, at the \textit{Indian Institute of Technology Guwahati, India.}
%
\entry*[$2024$] \hl{\textbf{Diploma Degree Sanskrit Linguist (July 2023 to June 2024):}} Certified by the \textit{Central Sanskrit University (CSU), Delhi, India,} organized by the Indian Knowledge Systems (IKS) in association with the \textit{Indian Institute of Technology Guwahati, India.}
%
\entry*[$2024$] \hl{\textbf{Active Participation in thirteen-day Interactive Video Lecture Sessions (April 24 to May 10):}} On \textit{Space Science and Technology Awareness Training (START) - Exploration of the Solar System} organized by the  \textit{Indian Space Research Organization (ISRO)} and conducted by the \textit{Indian Institute of Technology Guwahati, India,} as a Nodal Centre.
%
\entry*[$2023$] \hl{\textbf{Active Participation in Workshop (November 1):}} On \textit{Transitioning a Career in Cyber Security} organized by  \textit{Fixity EDX in association with Electronics and \& ICT Academy} of \textit{Indian Institute of Technology Guwahati, India}, supported by the \textit{Ministry of Electronics and Information Technology (MeitY), Government of India.}
%
\entry*[$2023$] \hl{\textbf{Certification Degree Sanskrit Linguist (July 2022 to June 2023):}} Certified by the \textit{Central Sanskrit University (CSU), Delhi, India,} organized by the  \textit{Indian Knowledge Systems (IKS)} in association with the \textit{Indian Institute of Technology Guwahati, India.}
%
\entry*[$2023$] \hl{\textbf{Active Volunteer and Teaching Assistant in organizing a seven-day high-end Workshop (June 24 to June 30):}} On \textit{Power Electronics Hardware Design with Microcontroller Programming} organized by the \textit{Indian Institute of Technology Guwahati, India} sponsored by the {Science and Engineering Research Board (SERB), India} under the Accelerate Vigyan scheme.
%
\entry*[$2022$] \hl{\textbf{Active Participation in two-day Workshop (December 19 to December 20):}} On \textit{High Performance Computing (HPC)} organized by the \textit{Indian Institute of Technology Guwahati, India} in collaboration with the \textit{Centre for Development of Advanced Computing (C-DAC), India.}
%
\entry*[$2022$] \hl{\textbf{Certified Karate Trainer and Fight Judge (November 20):}} \textit{Entry Level Kumite (fight) Judge} certified by the \textit{Karate India Organization (KIO)} affiliated with the \textit{Asian Karate Federation (AKF)} and the \textit{World Karate Federation (WKF),} recognized by the \textit{International Olympic Committee (IOC).}
%
\entry*[$2022$] \hl{\textbf{Certified Karate Practitioner (November 20):}} \textit{Second Dan Black Belt} awarded by the Traditional Shito-Ryu Karate Do Association (India), TSKA, approved by the \textit{Karate India Organization (KIO),} affiliated with the \textit{World Karate Federation (WKF),} recognized by the \textit{International Olympic Committee (IOC).}
%
\entry*[$2022$] \hl{\textbf{Active Participation in Lecture (November 03):}} On \textit{AI-Driven Networks for Earth and Space} organized by the \textit{Indian Institute of Technology Guwahati, India} in collaboration with the \textit{University of Illinois at Urbana Champaign (UIUC), USA.}
%
\entry*[$2022$] \hl{\textbf{Certified Participation in three-day Workshop (August 23 to August 25):}} On \textit{Scaling Blockchains: From Bitcoin to the Lightning Network} organized by the \textit{Indian Institute of Technology Guwahati, India} in collaboration with the \textit{University of Catania, Italy.}
%
\entry*[$2022$] \hl{\textbf{Certified Participation in ISEA Virtual Presentation Conclave (IVPC-2022) (June 23):}} On \textit{Modeling Attacks on Physically Unclonable Functions (PUFs)} and \textit{Open Trustless Blockchains: Security Trade-offs} organized by the \textit{Indian Institute of Technology Guwahati, India} in collaboration with the \textit{Ministry of Electronics and Information Technology (MeitY), Government of India.}
%
\entry*[$2022$] \hl{\textbf{Active Participation in Webinar (January 14):}} On \textit{Healthcare IoT} organized by the \textit{Indian Institute of Technology Guwahati, India} in collaboration with the \textit{IEEE Communication Society, Technical Committee on eHealth: Special Interest Group on `IoT for eHealth' and Technical Committee Green Computing and Communications: Special Interest Group on `Pandemics.'}
%
\entry*[$2022$] \hl{\textbf{Certified in Community Services (August 2021 Till Date):}} Active participation in social service ventures organized across the state of Assam, India organized by the \textit{National Service Scheme (NSS)} cell at the \textit{Indian Institute of Technology Guwahati, India.}
%
\entry*[$2021$] \hl{\textbf{Certified Participation in 4.0 Tech Online Bootcamp (September 02):}} On \textit{AI and ML, Cyber Security, IoT, Data Science, Augmented Reality (AR) and Virtual Reality (VR), Blockchain, Full Stack} organized by the \textit{Indian Institute of Technology Guwahati, India} in collaboration with \textit{NxtWave, CCBP 4.0 Certification Programs.}
%
\entry*[$2021$] \hl{\textbf{Certified Participation in Webinar (August 06):}} On \textit{Research Opportunities in Wind Technology} organized by the \textit{Indian Institute of Technology Guwahati, India} in collaboration with \textit{National Institute of Wind Energy (NIWE), Chennai, India.} with the support of the \textit{Ministry of New and Renewable Energy (MNRE), Government of India.}
%
\entry*[$2019$] \hl{\textbf{Certified Karate Practitioner (December 8):}} \textit{First Dan Black Belt} awarded by the Traditional Shito-Ryu Karate Do Association (India), TSKA, approved by the \textit{Karate India Organization (KIO),} affiliated with the \textit{World Karate Federation (WKF),} recognized by the \textit{International Olympic Committee (IOC).}
%
\entry*[$2006$] \hl{\textbf{Certified Swimmer:}} Awarded by the \textit{National Swimming Club, Kolkata, India.}





\subrubric{\textsc{\underline{Awards and Achievements}}}

\entry*[$2019$] \hl{\textbf{Participation Award:}} Several competitive and charitable running events.
%
\entry*[$2019$] \hl{\textbf{Service \& Commitment Award:}} Recognizing my persistent contributions to the organization.
%
\entry*[$2017$] \hl{\textbf{Merit Award:}} Numerous On the Spot awards for outstanding individual contributions.
%
\entry*[$2016$] \hl{\textbf{Service \& Commitment Award:}} Recognizing my persistent contributions to the organization.
%
\entry*[$2016$] \hl{\textbf{Merit Award:}} Numerous On the Spot awards for outstanding individual contributions.
%
\entry*[$2015$] \hl{\textbf{Merit Award:}} Numerous CLP Faculty awards for distinguished contribution towards knowledge building of associates.
%
\entry*[$2015$] \hl{\textbf{Merit Award:}} Numerous On the Spot awards for outstanding individual contributions.
%
\entry*[$2014$] \hl{\textbf{Merit Award:}} Numerous CLP Faculty awards for distinguished contribution towards knowledge building of associates.
%
\entry*[$2014$] \hl{\textbf{Service \& Commitment Award}: Recognizing my persistent contributions to the organization.
%
\entry*[$2013$] \hl{\textbf{Merit Award:}} Numerous CLP Faculty awards for distinguished contribution towards knowledge building of associates.
%
\entry*[$2011$] \hl{\textbf{Merit Award:}} Best Team of the Year in TCS Delhi-NCR region.
%
\entry*[$2006$] \hl{\textbf{Merit Award:}} Multiple Maths and Science Olympiads during my schooling.



\end{rubric}